\documentclass[10pt,english,ignorenonframetext,]{beamer}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
\usetheme[]{Boadilla}
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi
\newif\ifbibliography
\hypersetup{
            pdftitle={Pandoc some block examples},
            pdfauthor={Norman Markgraf},
            pdfborder={0 0 0},
            breaklinks=true}

% Prevent slide breaks in the middle of a paragraph:
\widowpenalties 1 10000
\raggedbottom

\AtBeginPart{
  \let\insertpartnumber\relax
  \let\partname\relax
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \let\insertsectionnumber\relax
    \let\sectionname\relax
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \let\insertsubsectionnumber\relax
  \let\subsectionname\relax
  \frame{\subsectionpage}
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
\input{moreblocks.tex}

\title{Pandoc some block examples}
\author{Norman Markgraf}
\date{}

\begin{document}
\frame{\titlepage}

\section{pandoc moreblocks example}\label{pandoc-moreblocks-example}

\begin{frame}{Give some more block types}

Three kind of new BlockTypes:

\begin{Beispiel}[One Example]\label{one-example}

This is a single example.

\end{Beispiel}

\begin{examples}[A couple of Examples]\label{a-couple-of-examples}

\begin{itemize}
\tightlist
\item
  This is a single example.
\item
  This is anotherone.
\end{itemize}

\end{examples}

\begin{definition}[A Definition Block]\label{a-definition-block}

The master Thesis:

\begin{equation*}
    e=mc^2
\end{equation*}

to be or not to be!

\end{definition}

\end{frame}

\begin{frame}{Next page}

\begin{theorem}[A Theorem]\label{a-theorem}

Yes! We need some! ;-)

\end{theorem}

\begin{Fakten}[Some facts]\label{some-facts}

\begin{itemize}
\tightlist
\item
  Mmmm
\item
  Maybe some more facts
\end{itemize}

\end{Fakten}

\begin{Fakt}[A fact]\label{a-fact}

Just a fact to believ!

\end{Fakt}

\end{frame}

\begin{frame}{Another page}

\begin{Uebung}[An exercise]\label{an-exercise}

Do it!

\end{Uebung}

\begin{Loesung}[The solution]\label{the-solution}

I did it!

\end{Loesung}

\begin{Lemma}[Lemma]\label{lemma}

Not the one of Zorn!

\end{Lemma}

\end{frame}

\begin{frame}{And another one}

\begin{Beweis}[Proof \ldots{}]\label{proof}

\ldots{} it or not!

\end{Beweis}

\end{frame}

\begin{frame}{The endblock tag:}

Normal Text

\begin{Bemerkung}[A Remark]\label{a-remark}

Some remarks

\end{Bemerkung}

Normal Text

\begin{Bemerkungen}[Some remarks]\label{some-remarks}

\begin{itemize}
\tightlist
\item
  One
\item
  Two
\item
  Three
\end{itemize}

\end{Bemerkungen}

\end{frame}

\begin{frame}[fragile]{The End!}

Well, much to do!

To process this try:

\begin{verbatim}
pandoc --from=markdown --to=json allblocks.md  | \
./moreblocks.py beamer | \
pandoc --from=json --to=beamer -s -o allblocks.pdf
\end{verbatim}

\end{frame}

\end{document}
